### 2017-09-18 manuscript/agg-intro.tex
Starting the objectives

Although there has been considerable effort to normalize and harmonize 
LCI database design methodology and data interchange \citep{UNEP_2011, JRC_ILCD_ELCD_2013, Mila_e_Canals_2015, Ingwersen_JLCA_2015}, less attention has been paid to harmonizing product system models.  These models are often highly complex and include countless modeling decisions, approximations, and assumptions made by a study author \citep{Lloyd2007, reap2008_I}.  Consequently, while comparative evaluations can be made regarding alternative cases or scenarios within a single study, comparisons across studies are much more challenging \citep{Heath2012, Henriksson2014}.  Even when relatively simple and homogeneous systems are considered, wide variations can be found in the results of studies from different authors \citep{van_der_Harst_2013, Turconi_2013}.
A lack of transparency in reporting, particularly regarding definitions of study scope and system boundary,
is a crucial challenge to the interpretation of results in comparative analysis \citep{Cleary2009, Laurent_2014}.
One consequence is the high cost and uneven rigor of critical review, in which the complexities of LCA come face to face with the limitations of current practice \citep{Curran2014}.

@@

@@

@@

 * A common theme in all these controversies is the inability for authors and their readers to formally agree on the structure and content of the product system model.

 * Although the general structure for life cycle assessment can be formally stated, there is no current practice for formally describing the product system model and thus, no formal mechanisms for interpretation or review of published LCA studies.

@@

 * The task of computing life cycle impact assessment (LCIA) results from a product system model is often described as an ``aggregation,'' in which the data in large, sparse models are combined through linear algebra operations into a small set of numeric scores.

@@

 * Although several equivalent methods for computing aggregated LCI and/or LCIA results have been described in the literature (Suh 2005; Lenzen 2007), the computational representation of product system models, and the generation of aggregated results, remains software-specific.

>>>>

Although there has been considerable effort to normalize and harmonize 
LCI database design methodology and data interchange \citep{UNEP_2011, JRC_ILCD_ELCD_2013, Mila_e_Canals_2015, Ingwersen_JLCA_2015}, less attention has been paid to harmonizing product system models.  These models are often highly complex and include countless modeling decisions, approximations, and assumptions made by a study author \citep{Lloyd2007, reap2008_I}.  Consequently, while comparative evaluations can be made regarding alternative cases or scenarios within a single study, comparisons across studies are much more challenging \citep{Heath2012, Henriksson2014}.  Even when relatively simple and homogeneous systems are considered, wide variations can be found in the results of studies from different authors \citep{van_der_Harst_2013, Turconi_2013}.
A lack of transparency in reporting, particularly regarding definitions of study scope and system boundary,
is a crucial challenge to the interpretation of results in comparative analysis \citep{Cleary2009, Laurent_2014}.  A further challenge to transparency can be found in the use of input data that are confidential or proprietary \citep{Kuczenski_2017}.  One consequence of all these challenges is the high cost and uneven rigor of critical review, in which the complexities of LCA come face to face with the limitations of current practice \citep{Curran2014}.

@@

An LCA study result is ultimately an assertion that for some constructed product model, the delivery of a particular reference flow is associated with a certain amount of environmental impact or potential impact.  But if the product model itself is ambiguously stated, then the significance of the result is ambiguous as well.  For a computational model to have scientific significance, its results need to be both verifiable and replicable by other scientists \citep{Fomel_2009, Mesirov_2010}.  But in the case of LCA, the structure and contents of the model are never stated precisely; instead they are \emph{described} in a written report, and the description must be interpreted by a reader.  When a study is reviewed, it is often the written report and \emph{not} the product system model itself that is the object of review.  In the end, there is no current practice that permits a reviewer to verify the correctness of the computations inherent in an LCA study if access to the product model itself is not available.

A common theme in all these controversies is the inability for authors and their readers to formally agree on the structure and content of the product system model.  Although the general structure for life cycle assessment can be stated formally, there is no current practice for formally describing the product system model and thus, no automatic mechanisms for interpretation or review of published LCA studies.

The purpose of this paper is to advance a framework for the formal description of product system models that would provide robust transparency and reproducibility of computed results.

The purpose of this paper is three-fold:
\begin{enumerate}[label=\roman*.]
\item to advance a fram
\item to describe the computation of aggregated LCIA results using a product system model as input data;
\item to show how the framework may be used to protect confidential information while still providing transparency and reproducibility during critical review.
\end{enumerate}

@@

o advance a framework for the formal description of a subset of LCA studies that can be used to document, validate, and reproduce the computations that lead from model specification to LCIA results.  The framework can also

But reproducibility of a computation requires a distinction between the computing algorithm and the input data \citep{Buckheit_1995, }; contemporary LCA lacks this distinction.

@@

@@

@@
